\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-21 notes/2loopNLSM.tex
fixed n vs N vs calN

Color-kinematics duality is a statement about the off-shell graphical
simplicity that manifests redundancy in the on-shell observables of
gauge and gravity theories. Ignoring factors of $i$ and the coupling
constant, the starting point to realize the duality is to express generic $m$-point $L$-loop amplitudes in a cubic graph representation:
\begin{equation}
  \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma n_\Gamma}{d_\Gamma} .
  \label{eq:gen-amp}
\end{equation}
Here the spacetime dimension is $D$.  Even though the underlying
theory may have quartic (or higher multiplicity) vertices, like NLSM and gravity, it is
possible to multiply and divide by propagators so that the sum runs
over the set of purely cubic graphs, $\Gamma$.  Overcounting is removed by
the internal symmetry factor $S_\Gamma$, which tracks the number of
graph symmetries with external legs held fixed.

The color factor
$c_\Gamma$ is the string of structure constants $f^{abc}$ associated
with the graph $\Gamma$,\footnote{This paper is focused on theories
  with particles that transform in the adjoint.  However, the double
  copy can be applied to a far more diverse set of theories with
  particles that transform in the fundamental or more diverse
  representations, see for example \cite{Johansson:2017srf,
    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,
    Carrasco:2023vjg}.}  the denominator $d_\Gamma$
is the product of propagators associated with the graph $\Gamma$, and
the numerator $n_\Gamma$ is all of the remaining kinematic factors
including dot products of momenta and polarization vectors.

In this form the color factors $c_\Gamma$ are not independent and are related to
one another via a set of Jacobi identities that look schematically
like
\begin{equation}
c_i+c_j+c_k=0,
\end{equation}
where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
the various kinematic numerators $n_\Gamma$ such that the numerators
obey the same Jacobi identities as the color factors
\begin{equation}
n_i +n_j +n_k=0.
\end{equation}
If color-kinematics duality can be achieved at the off-shell level,
then the kinematic numerators should satisfy an algebra just like the
color factors.  In theories where the kinematic algebra is known, it
is often the algebra of volume preserving diffeomorphisms
\cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz,
  Cheung:2021zvb, Cheung:2022mix}.
When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
As an example, the result of such a calculation for four-point NLSM pion scattering at tree level produces the numerators
\begin{align}
&n_s = s(t-u)\\
&n_t = t(u-s)\\
&n_u = u(s-t)
\end{align}
where the coupling has been normalized away.  These numerators sum to
zero by explicit calculation.  Note that the $s$-channel numerator
contains an explicit factor of $s$ that cancels with the propagator
and the same goes for the $t$- and $u$-channels so that the net result
is a local function, just as one would expect for the pion tree
amplitude.

Once color-dual numerators $n_\Gamma$ have been found, they can be
used to replace the color factors ($c_\Gamma \to n_\Gamma$) in a
\emph{different} amplitude to produce the corresponding amplitude in
a new colorless theory: \be\label{DCconstruction}
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{c_\Gamma
  \tilde{n}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(c_\Gamma \to n_\Gamma)}
~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{n_\Gamma
  \tilde{n}_\Gamma}{d_\Gamma}.
\end{equation}
This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
Importantly, the $\tilde{n}_\Gamma$ do not need to respect
color-kinematics duality.  The prototypical example of the double-copy
is that YM double copied with YM results in gravity where the gauge
invariance of each separate gluon produces the diffeomorphism
invariance of the graviton.  The double copy can be proven at tree
level using the KLT relations but there is significant evidence that
the double copy persists to all loop orders \cite{FiveLoopN4,
  GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
  KiermaierTalk}.  In addition to pointing at potential undiscovered
structure hidden in the Lagrangian for gravity, the double copy is
immensely useful at a utilitarian level since it is much more
efficient at producing $\mathcal{M}_m^L$ than traditional methods like
Feynman rules.

>>>>

Color-kinematics duality is a statement about the off-shell graphical
simplicity that manifests redundancy in the on-shell observables of
gauge and gravity theories. Ignoring factors of $i$ and the coupling
constant, the starting point to realize the duality is to express generic $m$-point $L$-loop amplitudes in a cubic graph representation:
\begin{equation}
  \mathcal{A}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int \frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma N_\Gamma}{d_\Gamma} .
  \label{eq:gen-amp}
\end{equation}
Here the spacetime dimension is $D$.  Even though the underlying
theory may have quartic (or higher multiplicity) vertices, like NLSM and gravity, it is
possible to multiply and divide by propagators so that the sum runs
over the set of purely cubic graphs, $\Gamma$.  Overcounting is removed by
the internal symmetry factor $S_\Gamma$, which tracks the number of
graph symmetries with external legs held fixed.

The color factor
$C_\Gamma$ is the string of structure constants $f^{abc}$ associated
with the graph $\Gamma$,\footnote{This paper is focused on theories
  with particles that transform in the adjoint.  However, the double
  copy can be applied to a far more diverse set of theories with
  particles that transform in the fundamental or more diverse
  representations, see for example \cite{Johansson:2017srf,
    Johansson2014zca, Johansson:2015oia, Johansson:2019dnu, Carrasco:2020ywq,
    Carrasco:2023vjg}.}  the denominator $d_\Gamma$
is the product of propagators associated with the graph $\Gamma$, and
the numerator $N_\Gamma$ is all of the remaining kinematic factors
including dot products of momenta and polarization vectors.

In this form the color factors $C_\Gamma$ are not independent and are related to
one another via a set of Jacobi identities that look schematically
like
\begin{equation}
C_i+C_j+C_k=0,
\end{equation}
where $i$, $j$, and $k$ are three graphs.  Example Jacobi relations
are presented in detail in \cref{sec:bootstrap}. The duality between color and kinematics is the statement that that there exists a way to rearrange factors between
the various kinematic numerators $N_\Gamma$ such that the numerators
obey the same Jacobi identities as the color factors
\begin{equation}
N_i +N_j +N_k=0.
\end{equation}
If color-kinematics duality can be achieved at the off-shell level,
then the kinematic numerators should satisfy an algebra just like the
color factors.  In theories where the kinematic algebra is known, it
is often the algebra of volume preserving diffeomorphisms
\cite{Monteiro2011pc, Ben-Shahar:2021zww, Cheung:2020djz,
  Cheung:2021zvb, Cheung:2022mix}.
When the kinematic algebra is not known explicitly, the kinematic numerators are typically constructed from an ansatz.
As an example, the result of such a calculation for four-point NLSM pion scattering at tree level produces the numerators
\begin{align}
&N_s = s(t-u)\\
&N_t = t(u-s)\\
&N_u = u(s-t)
\end{align}
where the coupling has been normalized away.  These numerators sum to
zero by explicit calculation.  Note that the $s$-channel numerator
contains an explicit factor of $s$ that cancels with the propagator
and the same goes for the $t$- and $u$-channels so that the net result
is a local function, just as one would expect for the pion tree
amplitude.

Once color-dual numerators $N_\Gamma$ have been found, they can be
used to replace the color factors ($C_\Gamma \to N_\Gamma$) in a
\emph{different} amplitude to produce the corresponding amplitude in
a new colorless theory: \be\label{DCconstruction}
\tilde{\mathcal{A}}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{C_\Gamma
  \tilde{N}_\Gamma}{d_\Gamma} ~~ \xrightarrow{(C_\Gamma \to N_\Gamma)}
~~ \mathcal{M}_m^L = \sum \limits_\Gamma \frac{1}{S_\Gamma} \int
\frac{d^{LD}\ell}{(2\pi)^{LD}} \frac{N_\Gamma
  \tilde{N}_\Gamma}{d_\Gamma}.
\end{equation}
This is known as the double-copy construction \cite{BCJ,Bern:2010ue,BCJreview}.
Importantly, the $\tilde{n}_\Gamma$ do not need to respect
color-kinematics duality.  The prototypical example of the double-copy
is that YM double copied with YM results in gravity where the gauge
invariance of each separate gluon produces the diffeomorphism
invariance of the graviton.  The double copy can be proven at tree
level using the KLT relations but there is significant evidence that
the double copy persists to all loop orders \cite{FiveLoopN4,
  GeneralizedDoubleCopyFiveLoops, Bern:2018jmv, Carrasco:2021otn, KLT,
  KiermaierTalk}.  In addition to pointing at potential undiscovered
structure hidden in the Lagrangian for gravity, the double copy is
immensely useful at a utilitarian level since it is much more
efficient at producing $\mathcal{M}_m^L$ than traditional methods like
Feynman rules.
